---
title: "Import_OlisData"
author:
- Douglas A. Campbell
- Sarah Gore
- Adrian Kryk
- Sylwia Sliwinska-Wilczewska
- Mireille Savoie
date: "`r format(Sys.Date())`"
output:
bookdown::html_document2:
    code_folding: show
    keep_md: yes
    toc: TRUE
    toc_float: TRUE
    toc_depth: 6
    fig_caption: yes
bibliography: [Manuscript_O2, RPackages.bib]
csl: plos-one.csl
editor_options: 
  markdown: 
    wrap: 72
---

# Set Chunk Options

```{r setup, include = FALSE}
knitr::opts_chunk$set(echo = TRUE, message = FALSE)
knitr::opts_chunk$set(fig.path='Figs/')
```

# Introduction

Import_OlisData.Rmd imports OLIS 14 UV/VIS Clarity spectrophotometer files from Data/RawData/OlisData.zip folder and stored in Data/ImportedData/ImportedOlisData folder as: 
PICO_Imported_OlisData.Rds

# Load Libraries and set Project Variables

```{r load libraries, warning = FALSE, echo=FALSE} 

library(lubridate)
library(broom)
library(knitr)
library(tidyverse)

```

```{r set project variables, read zipped files, list available files, warning = FALSE, echo=FALSE}
Project <- "PICO"
DataOut <- file.path("..", "Data", "ImportedData", "ImportedOlisData")

# Set the path to the zip folder and the destination folder
DataIn <- file.path("..", "Data", "RawData", "OlisData.zip")

#List files in the extracted folder with a ".asc" extension
OlisFiles <- unzip(DataIn, list = TRUE)
OlisFiles <- OlisFiles[grepl(".asc$", OlisFiles$Name), "Name"]
print(OlisFiles)

FileID <- "Smooth"
FileEncode <- "UTF-8" 
Delimiter <- ""
HeaderRows <- 0
```

# Set up fread_plus and read.delim_long function
```{r set up fread_plus and read.delim_long, warning = FALSE, echo=FALSE}
# Define function to read and process each file
fread_plus <- function(Flnm, Skip, FileEncode, Delim) {
  con <- unz(DataIn, Flnm)  # Corrected the file path within the zip archive
  data <- read.table(con, skip = Skip, encoding = FileEncode, sep = Delim, header = FALSE, row.names = NULL)
  
# Use tryCatch to handle errors during the closing of the connection
  tryCatch(
    close(con),
    error = function(e) {
      warning("Error closing connection: ", e$message)
    })
  
  data <- data %>%
    mutate(Filename = Flnm, CDateTime = ymd_hms(file.info(DataIn)$ctime)) 
  return(data)
}

#read.delim_long meant for map over a vector of filepaths to read, convert to long format and tidy the imported data
read.delim_long <- function(Flnm, FileEncode, Delimiter, HeaderRows){
  read.delim(Flnm, encoding = FileEncode, sep = Delimiter, skip = HeaderRows, header = FALSE, row.names = NULL) %>%
  mutate(Filename = flnm, CDateTime = ymd_hms(file.info(flnm)$ctime)) %>%
  mutate(FirstLastSpec = str_extract(Filename, "_[A-Z][a-z][A-Z][a-z][:digit:][:digit:][:digit:][:digit:]_[A-Z][a-z][A-Z][a-z][:digit:][:digit:][:digit:][:digit:]_")) %>%
  mutate(SampleNumbers = str_extract_all(FirstLastSpec, "[:digit:][:digit:][:digit:][:digit:]")) %>%
  mutate(FirstSampleNumber = as.numeric(map(SampleNumbers, ~.[[1]]))) %>%
  mutate(LastSampleNumber = as.numeric(map(SampleNumbers, ~.[[2]]))) %>%
  mutate(OperatorID = str_extract(Filename,"[A-Z][a-z][A-Z][a-z]")) %>%
  pivot_longer(cols = starts_with("X"), names_to = "SpectraID", values_to = "Abs") %>%
  mutate(SampleCode = as.numeric(str_remove(SpectraID, "X"))) %>%
  mutate(SampleNumber = SampleCode - min(SampleCode, na.rm = TRUE) + FirstSampleNumber) %>%
  relocate(OperatorID, SampleNumber) %>%
  unite(col = SampleID, OperatorID:SampleNumber, sep = "", remove = FALSE) %>%
  arrange(SampleID, nm) %>%
  relocate(SampleID, nm, Abs) %>%
  mutate(SpectraDate = str_extract(Filename, "/[:digit:][:digit:][:digit:][:digit:][:digit:][:digit:][:digit:][:digit:]_"),
         SpectraDate = str_remove_all(SpectraDate, "_"),
         SpectraDate = str_remove_all(SpectraDate, "/"),
         SpectraDate = ymd(SpectraDate)
  )
}
```

# Import and prepare files
```{r import OLIS Spectra corrected files, warning = FALSE, echo=FALSE}
TargetFile <-  OlisFiles

TargetSpectra <- TargetFile %>% 
  map_df(~fread_plus(Flnm = ., FileEncode = FileEncode, Delim = Delimiter, Skip = HeaderRows)) %>% 
  rename(OlisAbs_nm = `V1`,
          Absorbance = `V2`) %>% 
  filter(!is.na(Absorbance))  

TargetSpectraLong <- TargetSpectra %>%
  separate(col = Filename, into = c("ObsDate", "Project", "SampleID", "Range", "Type", "Correction", "Smooth"), sep = "([\\/\\_\\:])", remove = FALSE) 

TargetSpectraLong <- TargetSpectraLong %>%
  mutate(FilenameOlis = Filename) %>% 
  mutate(ObsDate = ymd(str_extract(ObsDate, "202[:digit:][:digit:][:digit:][:digit:][:digit:]"))) %>% 
  select(-c(Type, Correction, Smooth, Project, Filename, Range)) 
```

# Read MetaData
```{r read locally stored metadata from rds}
CultureCatalog <- readRDS(file = file.path("..", "Data","RawData" ,"CultureCatalog.Rds"))

CultureCatalog <- CultureCatalog %>% 
  select(-c(PrimaryOperator, Temp_c, ExpCul, ExpStartTime, Optode, OptodeCh, OptodeMeasure))
```

# Merge OlisSpectra with MetaData
```{r merge OlisSpectra with MetaData, warning = FALSE, echo=FALSE}
OLISSpectraMeta <- CultureCatalog %>%
  right_join(., TargetSpectraLong, by = c("SampleID" = "SampleID")) 

OLISSpectraMeta <- OLISSpectraMeta %>%
group_by(SampleID) %>%
  arrange(ObsDate) %>%
  mutate(E_days = as.numeric((ObsDate - ExpDate[1]))) %>%
  filter(!is.na(MC)) %>%
   select(-c(CDateTime)) %>% 
ungroup()

```


# Cleaning df before saving as rds and removed unnecessary files from the environment
```{r nest absorbance spectra}
OLISSpectraMeta <- OLISSpectraMeta %>% 
  nest(AbsSpectra = c(OlisAbs_nm, Absorbance)) 
```


```{r removed redundant df }
rm(CultureCatalog, TargetSpectra, TargetSpectraLong)
```

# Save rds for further analysis
```{r save rds}
saveRDS(OLISSpectraMeta, file.path(DataOut, paste(Project, "Imported_OlisData.Rds", sep = "_"), fsep = .Platform$file.sep), ascii = FALSE, version = NULL, compress = "xz", refhook = NULL)
```

# Variable names used in Data Dictionary
```{r}
colnames(OLISSpectraMeta)
```
