---
title: "Import_JazEmData"
author:
- Sylwia Sliwinska-Wilczewska
- Douglas A. Campbell
date: "`r format(Sys.Date())`"
output:
bookdown::html_document2:
    code_folding: show
    keep_md: yes
    toc: TRUE
    toc_float: TRUE
    toc_depth: 6
    fig_caption: yes
bibliography: BalticPhotoperiod.bib
csl: plos-one.csl
editor_options: 
  markdown: 
    wrap: 72
---

# Set Chunk Options

```{r setup, include = FALSE}
knitr::opts_chunk$set(echo = TRUE, message = FALSE)
knitr::opts_chunk$set(fig.path='Figs/')
```

# Introduction

Import_JazEmData.Rmd imports Jaz radiospectrometer files from Data/RawData/JazEmData.zip folder and stored in Data/ImportedData/ImportedJazEmData folder as: 
Baltic_Photoperiod_Imported_JazEmData.Rds

# Load Libraries and set Project Variables

```{r load libraries, warning = FALSE, echo=FALSE}
library(tidyverse)
library(lubridate)
library(googledrive)
```

```{r set project variables, read zipped files, list available files, warning = FALSE, echo=FALSE}
Project <- "Baltic_Photoperiod"
DataOut <- file.path("..", "Data", "ImportedData", "ImportedJazEmData")

# Set the path to the zip folder and the destination folder
zip_file <- file.path("..", "Data", "RawData", "JazEmData.zip")

# List files in the extracted folder with a ".txt" extension
Jazfile <- unzip(zip_file, list = TRUE)
Jazfile <- Jazfile[grepl(".txt$", Jazfile$Name), "Name"]
print(Jazfile)
```

# Set up fread_plus function

```{r set up fread_plus, warning = FALSE, echo=FALSE}
SkipCS <- 14
FileEncodeCS <- "UTF-8"
DelimCS <- "\t"
RollWindow <- 10

# Define function to read and process each file
fread_plus <- function(Flnm, Skip, FileEncode, Delim) {
  con <- unz(zip_file, Flnm)  # Corrected the file path within the zip archive
  data <- read.table(con, skip = Skip, encoding = FileEncode, sep = Delim, header = FALSE)
  
# Use tryCatch to handle errors during the closing of the connection
  tryCatch(
    close(con),
    error = function(e) {
      warning("Error closing connection: ", e$message)
    })
  
  data <- data %>%
    mutate(Filename = Flnm, CDateTime = ymd_hms(file.info(zip_file)$ctime)) 
  return(data)
}

# Use map_df to read and process all files in Jazfile
JazSpec <- Jazfile %>%
  map_df(~fread_plus(Flnm = ., Skip = SkipCS, FileEncode = FileEncodeCS, Delim = DelimCS))

# Rename columns
colnames(JazSpec)[1] <- "Wavelength"
colnames(JazSpec)[2] <- "Counts"
```

# Import and prepare files

```{r filename separation, warning = FALSE, echo=FALSE}
JazSpec <- JazSpec %>% 
  mutate(Filename = str_remove(Filename, pattern = " "))  %>% 
  separate(col = Filename, into = c("ObsDate", "Strain", "Par_ue", "WL"), sep = "([\\/\\/\\_\\_\\_\\_\\_\\_\\.])", remove = FALSE) %>% 
  mutate(FilenameJaz=Filename) %>% 
  select(-c("Filename"))

JazSpec <- JazSpec %>% 
mutate(ObsDate = ymd(ObsDate),
       Par_ue = as.numeric(Par_ue),
       WL = as.factor(WL))
```

# Select wavelength range from 400 to 700 nm

```{r select range of nm}
JazSpecTrim <- JazSpec %>% 
  subset(JazSpec$Wavelength >= 400 & JazSpec$Wavelength <= 701)
```

# Remove all NA columns & empty rows, fix column types

```{r remove empty rows and fix column types}
not_all_na <- function(x) {!all(is.na(x))}

JazSpecTrim <- JazSpecTrim %>%
  select_if(not_all_na)
```

# Find nm at max count and compare with rolling mean of counts

```{r find nm at max count}
JazSpecTrim <- JazSpecTrim %>% 
  group_by(WL, Strain) %>%
   mutate(rollmeanCounts = zoo::rollmean(Counts, k = RollWindow, align = "left", fill = NA),
          is_nm = round(Wavelength[which.max(Counts)]),
          is_nm_rollmean= round(Wavelength[which.max(rollmeanCounts)])) %>% 
  ungroup()
```

# Cleaning df before saving as rds and removed unnecessary files from the environment

```{r cleaning JazSpecTrim for final rds}
JazSpecTrim<-JazSpecTrim %>% 
  select(-c(CDateTime))

colnames(JazSpecTrim)
```

```{r removed unnecessary files from environment}
rm(JazSpec)
```

# Save rds for further analysis

```{r save rds}
saveRDS(JazSpecTrim, file.path(DataOut, paste(Project, "Imported_JazEmData.Rds", sep = "_"), fsep = .Platform$file.sep), ascii = FALSE, version = NULL, compress = "xz", refhook = NULL)
```

# Variable names used in Data Dictionary

```{r}
colnames(JazSpecTrim)
```
