---
title: "MultiDataImportTemplate"
author:
- Laurel Genge
- Carlie Barnhill
- Max Berthold
- Mireille Savoie
- Douglas A. Campbell
date: "`r format(Sys.Date())`"
output:
bookdown::html_document2:
    code_folding: show
    keep_md: yes
    toc: TRUE
    toc_float: TRUE
    toc_depth: 6
    fig_caption: yes
bibliography: Prochlorococcus_O2_NPQ.bib
csl: plos-one.csl
editor_options: 
  markdown: 
    wrap: 72
---

# Set Options

## Set figure caption font size

```{css, echo=FALSE}
p.caption {
  font-size: 18px;
}
```

## Set Chunk Options

```{r setup, include = FALSE}
knitr::opts_chunk$set(echo = TRUE, message = FALSE)
knitr::opts_chunk$set(fig.path='Figs/')
```

# To Do

-move filter for negative OD to point of log curve fitting Filtering
negative points needed for current noise filtering, so placed just
before noise filtering; with more sophisticated noise filtering -add
dynamic extraction of StartTime from first row of AbsTime Done

# Introduction

The PSI Multicultivator is used to grow 8 x 80 ml of phytoplankton
culture under a common temperature regime, with individual control of
bubbling, light level, light spectral quality and photoperiod for each
of the 8 culture tubes.

This .Rmd Rworkbook imports data in simple .csv long form exported from
PSI Multicultivators based upon project specific values for variables
set by the user.

It tidies and organizes the data. It uses a pivot_wider and
interpolation approach to get the Actinic_par and OD values in line
rowwise. This requires careful 'arrange' of the rows. It imports a
metadata Catalog and merges the metadata with the imported data based
upon shared values for the variables 'MC', 'Tube', and 'Filename' which
should unambiguously identify a given growth trajectory measured at
OD680 or OD720.

It generates preliminary data plots. It filters the data for outliers by
screening out values distant from the moving average of a window in the
stream; this requires careful 'arrange' of the rows so sequential rows
represent sequential time steps.

This works because the OD680 & OD720 data are only episodically, but
widely, aberrant when a bubble interrupts the measurement, and if the
MultiCultivator is running properly these bubble aberration events are
rare.

# Load Libraries and set Project Variables

```{r load libraries}
# libraries; Note check actual dependencies
library(tidyverse)
library(lubridate)
library(broom)
library(knitr)
library(zoo)
library(data.table)
library(googledrive)
library(googlesheets4)

```

```{r set project variables}
#"..", takes up a level in the directory path
Project <- "PICO"
DataIn <- file.path("..","MultiCultiData")
PlotsPath <- file.path("..","Plots")
DataOut <- file.path("..","ImportedData")
#MetaCatalog <- file.path("..","PicoCatalog.csv")

Sensor <- "od-680"

#interactively set the hour of day at which photoperiod starts for later generation of ToD Time of Day
#replaced by dynamic extraction from the first row of the AbsTime column in the datafile
#StartHour <- 7

```

```{r set colours}
MyWavelengths = c(405, 450, 475, 530, 615, 660, 730, "WW")
MCMIXColours = c("violet", "darkblue", "dodgerblue", "green","orange","red","purple", "black")

names(MCMIXColours) <- MyWavelengths
MCMIXColours

# SensorWavebands = c(680, 720)
# SensorColours = c("red", "black")
# names(SensorColours) <- SensorWavebands
# 
# SensorColours
```

# Import MetaData 
```{r load Catalog direct from googlesheet, results = "hide"}
# #implement read with googlesheet name instead of full url

gs4_deauth()

# imagine this is the URL or ID of a Sheet readable by anyone (with a link)


Catalog <- read_sheet("https://docs.google.com/spreadsheets/d/1ZXpwR7Gfto-uRzVdXzMpQF4frbrvMLH_IyLqonFZRSw/edit#gid=0") %>% 
   
  # read_sheet has an annoying "feature" to set the type of columns it can't parse to a list.
  # ggplot/dplyr doesn't like working with a dataframe of lists.
  # In this case WL is set to a list since some values are numbers, some are strings, some are blank.
  # To fix this, first drop all rows missing WL, then unlist.
  # Must first drop NA rows since unlist will collapse NULL lists, then the unlisted WL is a shorter length than original WL column, which mutate doesn't like.
  drop_na(WL) %>%
  mutate(WL = unlist(WL))

as.data.frame(Catalog)

Catalog <- Catalog %>%
   mutate(ExpDate = ymd(ExpDate),
          ExpEndDate = ymd_hms(`ExpEndDate`))

```

# List previously imported files

```{r previously imported files}
list.files(path = DataOut, pattern = Project, full.names = TRUE)
```

# List MultiCulti files

for Project that are saved in DataIn and Previously Processed Files

```{r MultiCulti files}
MultiFiles <- list.files(path = DataIn, pattern = Project, full.names = TRUE)

#check file names
MultiFiles

```

# Set Target File

Could implement function to list difference between
unique(GrowthSummaryAppend\$Filename) and MultiFiles if needed later;
scan visually to set TargetFile for now.



```{r set TargetFile}
TargetFile <- "../MultiCultiData/20230413_PICO_MCMIX004_RUN113.csv"



TargetFileName <- str_split(string = TargetFile, "/")[[1]][3] %>%
  str_remove(pattern = ".csv")

TargetFileName
```

## Create function using data.table::fread to skip the beginning comments and starts reading file after key word Skip

```{r fread_plus}
fread_plus <- function(Flnm, Skip){data.table::fread(file = Flnm, skip = Skip) %>%
    mutate(Filename = Flnm, CDateTime = ymd_hms(file.info(Flnm)$ctime))
}
```

# Read in TargetFile

select(-c(V5)) only needed for some files.

```{r Read TargetFile}
#abs-time is failing because it contains ',' in the variable values; file is actually a .tsv, not a .csv
#abs-time not currently used?
# TargetData <- fread_plus(Flnm = TargetFile, Skip = "key") %>%
# select(-c(V5))

#run this if V5 is the 'value' column
TargetData <- fread_plus(Flnm = TargetFile, Skip = "key")  %>%
   select(-c(V5))

# %>%
#  select(-c(value)) %>%
#   rename(value = V5)


TargetData[1:10,]

#check whether all necessary values for 'key' are present; people forget to 'export all' values from PSI
unique(TargetData$key)
```

```{r read in all MultiData}
# MultiData <- MultiFiles %>%
#   map_df(~fread_plus(Flnm = ., Skip = "key")) %>%
#   select(-c(V5))
# 
# MultiData[1:10,]

# MultiDataTarget <- MultiData %>%
   #filter(Filename == TargetFile)
```

```{r TargetFile actinic light NA to 0}
# TargetData <- TargetData %>%
#   mutate(value = if_else(grepl("actinic-lights", key), if_else(is.na(value), 0, value), value))

```

# Filter superfluous rows, Add ToD column, extract ExpDate, extract MC, 

```{r tidy MultiDataTarget}
#filter superfluous rows to simplify later pivot
TargetData <- TargetData %>%
  # filter(key != "thermo.temperature",
  #        key !="thermo.thermo-reg",
  #        key != "mc-airpump.airpump") %>%
  filter(str_detect(key, "od-720|od-680|actinic-lights.light"))

TargetData <- TargetData %>%
  select(key, time, `abs-time`, value, Filename, CDateTime) %>%
  mutate(Tube = str_extract(key, "-[:digit:]"),
         Tube = as.numeric(str_extract(Tube, "[:digit:]")),
         abs_time = dmy_hms(`abs-time`)) %>%
  select(-`abs-time`)

#extract StartHour dynamically from first row of abs_time and display for cross check
StartHour <- as.numeric(format(TargetData$abs_time[1], format = "%H"))
StartHour
 
StartDate <- TargetData$abs_time[1]
StartDate

#Generate ToD as mod 24 of time + StartHour
TargetData <- TargetData %>%
  mutate(ToD = (time + StartHour) %% 24,
         Day = round((time/24), digits = 0))
#had trouble extracting 'Day' from abs_time, only got 3 unique values
  
#extract ExpDate for matching with Catalog
TargetData <- TargetData %>% 
    mutate(ExpDate = str_extract(Filename, "/202[:digit:][:digit:][:digit:][:digit:][:digit:]_"),
           ExpDate = ymd(str_extract(ExpDate, "202[:digit:][:digit:][:digit:][:digit:][:digit:]")))

#extract MC for matching with Catalog
#fixed to run with MC or MCMIX.
#fixed to work for RUN #'s > 100. MC extracted from filename when Runs >99 returns the MC name and RUN #, this removes '_RUN#'
TargetData <- TargetData %>% 
    mutate(MC = str_extract(Filename, "MC.*[:digit:][:digit:][:digit:]"),
           MC = str_remove(MC, pattern = "\\_.*"))

#Run this if Run number exceeds 99.  MC extracted from filename when Runs >99 returns the MC name and RUN #, this removes '_RUN#'


#add ln(value) later


```

## Create preliminary plot for TargetData

```{r prelim plot}
#Run <- c("MultiCulti/20200124_PICO_MCMIX004_RUN1.csv", "MultiCulti/20200124_PICO_MCMIX006_RUN2.csv")

# TargetDataPlotPrelim <- 
  TargetData %>%
  filter(grepl("od-", key)) %>%
  #filter(grepl("od-sensors-", key)) %>%
  ggplot(data = .) +
  geom_point(aes(x = time, y = value, colour = as.factor(str_detect(key, "680"))), size = 0.5) +
  #scale_x_continuous(breaks=seq(0, 800, by = 125)) + 
  #coord_cartesian(xlim = c(-5, 800)) +
  geom_vline(aes(xintercept = 7 * 24), linetype = "dashed") + 
  geom_vline(aes(xintercept = 14 * 24), linetype = "dashed") + 
  scale_colour_manual(values = c("black", "red")) +
  labs(y = "Optical Density (OD)", x = "Elapsed Time (h)", title = "Tubes") +
  facet_grid(cols = vars(as.factor(Tube))) +
  theme_bw() 

# + 
#     theme(legend.position="none")

# TargetDataPlotPrelim

#cols = vars(Filename), 

#, fill = if_else(str_detect(key, "680"), "red", "black")

#
```

## Save Preliminary Plot to PlotsPath folder if desired

Generates .png for later presentation if needed.

```{r save preliminary plot as .png to folder}

 # ggsave(file = file.path(PlotsPath, paste(TargetFileName, "TargetDataPlotPrelim",".png",sep = "")), plot = TargetDataPlotPrelim, device = NULL, scale = 1, height=10, width= 20, units = c("cm"),dpi = 300, limitsize = TRUE)
```

# Generate par_ue column with rows aligned with OD measures

Pivot_wider to get actinic-lights data aligned with relevant sensor
data. Why are there NULL values in the OD sensor columns? Should always
have a value? Import issue? Misalignment b/t light and OD? Need to
include arrange(Filename, time, Tube) to keep things aligned! Need to
group_by and/or reorder rows appropirately; Be Careful

```{r pivot_wider}
#possible issue with data structure; there are multiple values for some of the rows of actinic light columns, so the column becomes a list.
#Can add  values_fn = 
#to arbitrarily take the max or min etc. element of the list; but there might be a wider problem here when importing multiple files

TargetDataWide <- TargetData %>%
  pivot_wider(names_from = key, values_from = value, values_fn = list(value = max)) %>%
  arrange(Filename, MC, Tube, time)

TargetDataWide[1:10,]

rm(TargetData)
```

Actinic light values do not align time wise with OD measures.
Interpolate NA in actinic light columns from last observation, arrange
by MC & Tube Then generate Actinic_par summary column If multiple lights
are activated this chunk will give the summed par of all different
colours for the tube. If a single actinic light is activated per tube,
this gives the par for that tube. Filter rows where !is.na(Actinic_par)
to check for incorrect row sums.

Interpolation for Sine is not necessarily appropriate interpolation for
Square photoregime; issues with propagating last Actinic_par of
afternoon through evening, or back-casting first Actinic_par of morning.

Small glitching adding actinic_light values for tubes where
actinic_light column should be 0; issue with interpolation we think.

```{r interpolate and summarize actinic_par by tube}
#http://publish.illinois.edu/spencer-guerrero/2014/12/11/2-dealing-with-missing-data-in-r-omit-approx-or-spline-part-1/

#https://dplyr.tidyverse.org/dev/articles/colwise.html

#Interpolation causes problems with final rows that repeat last value.

interpolate <- function(x){zoo::na.locf(x, na.rm = FALSE, fromLast = FALSE, type = "l", maxgap = Inf)}

#possible problem with actinic_par for MC data b/c actinic-lights.light1 = NA generates actinic_par of 0 b/c in rowSums na.rm = TRUE, which treats NA as 0.
#possibly not a big problem but watch for bugs
#na.rm = FALSE fails to run
TargetDataWide <- TargetDataWide %>%
  group_by(Tube) %>%
  arrange(Filename, MC, Tube, time) %>%
  mutate(across(.cols = starts_with("actinic-lights.light"), .fns = interpolate)) %>%
  ungroup() %>%
  mutate(Actinic_par = rowSums(.[grep("actinic-lights.light", names(.))], na.rm = TRUE)) %>%
  filter(!is.na(Actinic_par)) %>%
   select(!contains("actinic-lights.light"))

#drop original actinic light columns?
# select(!contains("actinic-lights.light")) 

TargetDataWide[1:10,]
```

Now that Actinic_par is aligned with each row, coalesce
od-sensors-X.od-720 and od-sensors-X.od-680 into 2 columns, b/c 'Tube'
is already a column, so no need to identify tube X in
od-sensors-X.od-680 columns. This might cause problems later matching OD
measures to actinic light colours. Filter out rows where OD \<= 0

```{r consolidate OD}
TargetDataWide <- TargetDataWide  %>%
   mutate(OD680 = rowSums(.[grep("od-680", names(.))], na.rm = TRUE),
          OD720 = rowSums(.[grep("od-720", names(.))], na.rm = TRUE)) %>%
   select(!contains("od-sensors"))
  # filter(OD680 > 0,
  #        OD720 > 0

#move filtering for OD680 >0 until just before curve fitting to avoid data structure problems
TargetDataWide[1:10,]

```

# Merge Data with meta data

```{r metadata merge}
#This generates 'NA' values for ~1,000,000 rows of 'O2'; possibly the temperature rows?
TargetDataMeta <- left_join(x = TargetDataWide, y= Catalog, by = c("ExpDate", "MC", "Tube"), suffix  = c("_multi", "_cat"))

TargetDataMeta

rm(TargetDataWide)
```

```{r second prelim plot}
#TargetDataPlotFacet <- 
  TargetDataMeta %>% ggplot() +
  geom_point(aes(x = time, y = OD680, colour = as.factor(WL)), size = 0.15) +
  geom_point(aes(x = time, y = OD720), size = 0.15, colour = "orange") +
  #geom_point(aes(x = time, y = Actinic_par/1000),  colour = "orange", size = 0.0001) +
  geom_vline(aes(xintercept = 7 * 24), linetype = "dashed") + 
  geom_vline(aes(xintercept = 14 * 24), linetype = "dashed") + 
  #scale_x_continuous(breaks=seq(0, 800, by = 125)) +
  #coord_cartesian(xlim = c(-10, 800)) +
  scale_colour_manual(values = MCMIXColours) +
  labs(y = "Optical Density (OD)", x = "Elapsed Time (h)", subtitle = "Growth Light (µE); Strain; ID; Tube") +
  facet_grid(rows = vars(as.factor(O2)), cols = vars(as.factor(Tube), as.factor(Par_ue),Strain, ID)) +
  theme_bw() +  
  labs(colour = "Actinic PAR (nm)")

#TargetDataPlotFacet

```

Run this chunk only for tubes with OD680 and/or OD720 < 0
This will keep record of tubes even if they did not grow or had negative growth. These tubes get filtered out later if you do not run this chunk
Remember to comment out after use 
```{r, Add dummy points if a tube has OD values less than zero}

# TargetDataMeta <- TargetDataMeta %>%
# mutate(OD680 = if_else(Tube == 1, 0.005, OD680),
#        OD720 = if_else(Tube == 1, 0.003, OD720))

```

Run this chunk if some tubes have poor data
This is bad practice;
Only use if light recordings were actually wrong
Consider a rule-based filtering to eliminate points after curve reaches peak
```{r filter aberrant tube(s)}
# TargetDataMeta <- TargetDataMeta %>%
#   filter(Tube != 1) %>%
#   filter(Tube != 8)
# 
# TargetDataMeta5 <- TargetDataMeta %>%
#   filter(Tube == 5,
#          time <= 300)
# 
# TargetDataMeta <- TargetDataMeta %>%
#   filter(Tube != 5) %>%
#   rbind(., TargetDataMeta5)
# 
# TargetDataMeta %>% ggplot() +
#   geom_point(aes(x = time, y = OD680, colour = as.factor(WL)), size = 0.1) +
#   geom_point(aes(x = time, y = OD720), size = 0.01, alpha = 0.1, colour = "black") +
#   geom_point(aes(x = time, y = Actinic_par/1000),  colour = "orange", size = 0.0001) +
#   geom_vline(aes(xintercept = 7 * 24), linetype = "dashed") + 
#   geom_vline(aes(xintercept = 14 * 24), linetype = "dashed") + 
#   #scale_x_continuous(breaks=seq(0, 800, by = 125)) +
#   #coord_cartesian(xlim = c(-10, 800)) +
#   #scale_colour_manual(values = MCMIXColours) +
#   labs(y = "Optical Density (OD)", x = "Elapsed Time (h)", subtitle = "Growth Light (µE); Strain; ID; Tube") +
#   facet_grid(rows = vars(as.factor(O2)), cols = vars(as.factor(Tube), as.factor(Par_ue),Strain, ID)) +
#   theme_bw() +  
#   labs(colour = "Actinic PAR (nm)")

```

## Save second preliminary plot if desired

```{r save second preliminary plot as .png to folder}

 # ggsave(file = file.path(PlotsPath, paste(TargetFileName, "TargetDataPlotFacet",".png",sep = "")), plot = TargetDataPlotFacet, device = NULL, scale = 1, height=10, width= 20, units = c("cm"),dpi = 300, limitsize = TRUE)
```

# Filter OD outliers

Rewrite with Time Series tools?? Filtering messes up unless - values
removed b/c of divisions

Experiment end times are tube specific taken from metacatalog
StartDate taken from first abs_time point from MC software

MAD is median absolute deviation Used median as opposed to mean to filter anomalous OD values due to affects of bubbling interference because determining outliers from the mean in a given window with many outliers were not detected since deviations from the mean were low. 
```{r filter bad OD and data points after experiment end time }

#moving average screen
MovAvgScreen <- 6
MovAvgWindow <- 20

TargetDataMetaFilter <- TargetDataMeta %>%
  filter(OD680 > 0) %>% # consider this rule for OD720 as well
  group_by(ID) %>%
  arrange(Filename, MC, Tube, time) %>%
  mutate(ExpEndHour = (difftime(ExpEndDate, StartDate, units = "hours"))) %>%
   mutate(TimeFlag = case_when(time >= ExpEndHour  ~ 1, 
                              time < ExpEndHour ~ 0)) %>%
  mutate(MovMedian680 = rollapply(OD680, MovAvgWindow, median, fill = "extend",  align = "left"),
         MovMedian720 = rollapply(OD720, MovAvgWindow, median, fill = "extend",  align = "left"),
         MovMAD680 = rollapply(OD680, MovAvgWindow, mad, fill = "extend",  align = "left"), 
         MovMAD720 = rollapply(OD720, MovAvgWindow, mad, fill = "extend",  align = "left"), 
         IsMovMAD680Outlier = if_else(OD680 > MovMedian680 + (MovMAD680 * MovAvgScreen) | OD680 < MovMedian680 - (MovMAD680 * MovAvgScreen), 1,0),
         IsMovMAD720Outlier = if_else(OD720 > MovMedian720 + (MovMAD720 * MovAvgScreen) | OD720 < MovMedian720 - (MovMAD720 * MovAvgScreen), 1,0))


         # OD680 = if_else(OD680 > MovMedian680 + (MovMAD680 * MovAvgScreen) | OD680 < MovMedian680 - (MovMAD680 * MovAvgScreen), MovMedian680, OD680), #consider replacing OD680 and OD720 rather than filter
         # OD720 = if_else(OD720 > MovMedian720 + (MovMAD720 * MovAvgScreen) | OD720 < MovMedian720 - (MovMAD720 * MovAvgScreen), MovMedian720, OD720)


print(paste("Outliers caught by IsMovMAD680Outlier filter:",
            sum(TargetDataMetaFilter$IsMovMAD680Outlier, na.rm = TRUE)))
print(paste("Outliers caught by IsMovMAD720Outlier filter:",
            sum(TargetDataMetaFilter$IsMovMAD720Outlier, na.rm = TRUE)))

TargetDataMetaFilter <- TargetDataMetaFilter %>%
  filter(
    !is.na(IsMovMAD680Outlier),
    !is.na(IsMovMAD720Outlier),
    IsMovMAD680Outlier == 0,
    IsMovMAD720Outlier == 0
         )%>%
    filter(TimeFlag == 0) 

# "actinic-lights.light"

#rm(TargetDataMeta)
```

```{r filterdataplot}

TargetDataMetaFilterPlot <- TargetDataMetaFilter %>% 
  ggplot() +
  geom_point(aes(x = time, y = OD680, colour = as.factor(WL)), size = 0.15) +
  geom_point(aes(x = time, y = OD720), size = 0.15, colour = "orange") +
  geom_vline(aes(xintercept = 7 * 24), linetype = "dashed") + 
  geom_vline(aes(xintercept = 14 * 24), linetype = "dashed") + 
  #geom_point(aes(x = time, y = Actinic_par/1000),  colour = "orange", size = 0.0001) +
 # geom_point(aes(x = time, y = IsMovAvgOutlier680)) +
#scale_x_continuous(limits = c(0,100))+
  #scale_x_continuous(breaks=seq(0, 800, by = 125)) +
  #coord_cartesian(xlim = c(-10, 800)) +
  scale_colour_manual(values = MCMIXColours) +
  labs(y = "Optical Density (OD)", x = "Elapsed Time (h)", subtitle = "Growth Light (µE); Strain; ID; Tube") +
 facet_grid(rows = vars(as.factor(O2)), cols = vars(as.factor(Tube), as.factor(Par_ue),Strain, ID)) +
  theme_bw() +  
  labs(colour = "Actinic PAR (nm)")

TargetDataMetaFilterPlot
```

Supplementary Growth Plot
```{r, fig.height = 6, fig.width = 4}

# ExpandTube = 1
# OD680_x = median(TargetDataMetaFilter$time)
# OD720_x = median(TargetDataMetaFilter$time)
# OD680_y = as.numeric(TargetDataMetaFilter %>% ungroup() %>% filter(Tube == ExpandTube, time == OD680_x) %>% select(OD680)) + 0.2
# OD720_y =  as.numeric(TargetDataMetaFilter %>% ungroup() %>% filter(Tube == ExpandTube, time == OD680_x) %>% select(OD720))
# TargetDataMetaFilterExpandPlot <- TargetDataMetaFilter %>%
#   filter(Tube == ExpandTube) %>%
#   ggplot() +
#   geom_point(aes(x = time, y = OD680), colour = "darkgreen", size = 0.1) +
#   geom_point(aes(x = time, y = OD720), size = 0.1, alpha = 0.1, colour = "blue") +
#   scale_y_continuous(breaks=seq(0, 1.0, by = 0.2)) +
#   coord_cartesian(ylim = c(0, 1.0)) +
#   scale_colour_manual(values = MCMIXColours) +
#   labs(y = "Optical Density (OD)", x = "Elapsed Time (h)") +
#   ggh4x::facet_nested(rows = vars(WL), cols = vars(Strain, Par_ue), labeller = labeller(Ex_WL = label_both, strain = label_value, Par_ue = label_both, WL = label_both, Photoperiod = label_both)) +
#   theme_bw()
# TargetDataMetaFilterExpandPlot
# 
# 
# 
# Par_ue.labs <- c("Growth Light Intensity: 60 µE")
# names(Par_ue.labs) <- c("60")
# WL.labs <- c("Growth Color Light: 660 nm")
# names(WL.labs) <- c("660")
# ExpandTube = 1
# OD680_x = median(TargetDataMetaFilter$time)
# OD720_x = median(TargetDataMetaFilter$time)
# OD680_y = as.numeric(TargetDataMetaFilter %>% ungroup() %>% filter(Tube == ExpandTube, time == OD680_x) %>% select(OD680)) + 0.2
# OD720_y =  as.numeric(TargetDataMetaFilter %>% ungroup() %>% filter(Tube == ExpandTube, time == OD680_x) %>% select(OD720))
# TargetDataMetaFilterExpandPlot <- TargetDataMetaFilter %>%
#   filter(Tube == ExpandTube) %>%
#   ggplot() +
#   geom_point(aes(x = time, y = OD680), colour = "darkgreen", size = 0.1) +
#   geom_point(aes(x = time, y = OD720), size = 0.1, alpha = 0.1, colour = "blue") +
#   scale_y_continuous(breaks=seq(0, 1.0, by = 0.2)) +
#   coord_cartesian(ylim = c(0, 1.0)) +
#   scale_colour_manual(values = MCMIXColours) +
#   labs(y = "Optical Density (OD)", x = "Elapsed Time (h)") +
#   ggh4x::facet_nested(cols = vars(Strain, WL, Par_ue), labeller = labeller(strain = label_value, Photoperiod = label_both, Par_ue = Par_ue.labs, WL = WL.labs)) +
#   # annotate(geom = "text", x = OD680_x, y = OD680_y, label = ""~OD[680]~"", size = 4.5, colour = "darkgreen", vjust = -14.5, hjust = 2.5) +
#   # annotate(geom = "text", x = OD720_x, y = OD720_y, label = ""~OD[720]~"", size = 4.5, colour = "blue", vjust = -20, hjust = 2.5) +
# theme_bw() +
# theme(strip.text.x = element_text(size = 12),
#       strip.text.y = element_text(size = 12),
#       #strip.background = element_rect(color="black", size=0.5, linetype="solid"),
#       axis.text = element_text(size = 12),
#       axis.title = element_text(size = 12))
# 
# # theme(strip.background = element_rect(color="black", size=1.5, linetype="solid"))
# 
# TargetDataMetaFilterExpandPlot
# # grob <- grobTree(textGrob("Scatter plot", x=0.1,  y=0.95, hjust=0,
# #   gp=gpar(col="red", fontsize=13, fontface="italic")))
# #annotation_custom(grob)+facet_wrap(~cyl, scales="free")
# 
# 
# 
# #labelling dynamically offset from data traces.
# #use 'median' for 'x' and OD680 + offset for 'y'
# ExpandTube = 1
# OD680_x = median(TargetDataMetaFilter$time)
# OD720_x = median(TargetDataMetaFilter$time) 
# Light_x = max(TargetDataMetaFilter$time) - 200
# 
# OD680_y = as.numeric(TargetDataMetaFilter %>% ungroup() %>% filter(Tube == ExpandTube, time == OD680_x) %>% select(OD680)) + 0.2
# 
# OD720_y =  as.numeric(TargetDataMetaFilter %>% ungroup() %>% filter(Tube == ExpandTube, time == OD680_x) %>% select(OD720))
# 
# Light_y = as.numeric(TargetDataMetaFilter %>% ungroup() %>% filter(Tube == ExpandTube, time == OD680_x) %>% select( Actinic_par))/1000 + 0.1
# 
# TargetDataMetaFilterExpandPlot <- TargetDataMetaFilter %>% 
#   filter(Tube == ExpandTube) %>%
#   ggplot() +
#   geom_point(aes(x = time, y = OD680), size = 0.1, colour = "darkgreen") +
#   geom_point(aes(x = time, y = OD720), size = 0.1, alpha = 0.1, colour = "blue") +
#   scale_y_continuous(breaks=seq(0, 1.0, by = 0.2)) +
#   coord_cartesian(ylim = c(0, 1.0)) +
#   
#   # scale_x_continuous(breaks=seq(0, 250, by = 50)) +
#   # coord_cartesian(xlim = c(0, 250)) +
#   
#   scale_colour_manual(values = MCMIXColours) +
#   geom_point(aes(x = time, y = Actinic_par/1000), colour = "orange",  size = 0.0001) +
#   #geom_vline(aes(xintercept = 7 * 24), linetype = "dashed") + 
#   #geom_vline(aes(xintercept = 14 * 24), linetype = "dashed") + 
#   # scale_x_continuous(breaks=seq(0, 800, by = 125)) +
#   # coord_cartesian(xlim = c(0, 800)) +
#   labs(y = "Optical Density (OD)", x = "Elapsed Time (h)") +
#   #facet_grid(rows = vars(O2), cols = vars(Tube, Par_ue, Strain, ID)) +
#   ggh4x::facet_nested(cols = vars(Strain, WL, Par_ue), labeller = labeller(strain = label_value, Photoperiod = label_both, Par_ue = Par_ue.labs, WL = WL.labs)) +
#   #annotate(geom = "text", x = OD680_x, y = OD680_y, label = "OD680", size = 5, colour = "darkgreen") +
#   #annotate(geom = "text", x = OD720_x, y = OD720_y, label = "OD720", size = 5, colour = "blue") +
#   #annotate(geom = "text", x = Light_x, y = Light_y, label = "Light level", size = 5, colour = "orange") +
#   theme_bw() +
#   theme(strip.text.x = element_text(size = 12),
#       strip.text.y = element_text(size = 12),
#       axis.text = element_text(size = 12),
#       axis.title = element_text(size = 12))
#   labs(colour = "Actinic PAR (nm)")
# 
# TargetDataMetaFilterExpandPlot 



```

```{r filterdataplotexpand}
#labelling dynamically offset from data traces.
#use 'median' for 'x' and OD680 + offset for 'y'
ExpandTube = 1
OD680_x = median(TargetDataMetaFilter$time)
OD720_x = median(TargetDataMetaFilter$time) 
Light_x = max(TargetDataMetaFilter$time) + 100

OD680_y = as.numeric(TargetDataMetaFilter %>% ungroup() %>% filter(Tube == ExpandTube, time == OD680_x) %>% select(OD680)) + 0.2

OD720_y =  as.numeric(TargetDataMetaFilter %>% ungroup() %>% filter(Tube == ExpandTube, time == OD680_x) %>% select(OD720))

Light_y = as.numeric(TargetDataMetaFilter %>% ungroup() %>% filter(Tube == ExpandTube, time == OD680_x) %>% select( Actinic_par))/1000 + 0.1

TargetDataMetaFilterExpandPlot <- TargetDataMetaFilter %>% 
  filter(Tube == ExpandTube) %>%
  ggplot() +
  geom_point(aes(x = time, y = OD680, colour = as.factor(WL)), size = 0.1) +
  geom_point(aes(x = time, y = OD720), size = 0.1, alpha = 0.1, colour = "blue") +
  scale_colour_manual(values = MCMIXColours) +
  geom_point(aes(x = time, y = Actinic_par/1000), colour = "orange",  size = 0.0001) +
   geom_vline(aes(xintercept = 7 * 24), linetype = "dashed") + 
  geom_vline(aes(xintercept = 14 * 24), linetype = "dashed") + 
  # scale_x_continuous(breaks=seq(0, 800, by = 125)) +
  # coord_cartesian(xlim = c(0, 800)) +
  labs(y = "Optical Density (OD)", x = "Elapsed Time (h)",subtitle = "Growth Light (µE); Strain; ID; Tube") +
  facet_grid(rows = vars(O2), cols = vars(Tube, Par_ue, Strain, ID)) +
  annotate(geom = "text", x = OD680_x, y = OD680_y, label = "OD680", size = 5, colour = "darkblue") +
  annotate(geom = "text", x = OD720_x, y = OD720_y, label = "OD720", size = 5, colour = "black") +
  annotate(geom = "text", x = Light_x, y = Light_y, label = "Light level", size = 5, colour = "orange") +
  theme_bw() +
  labs(colour = "Actinic PAR (nm)")

TargetDataMetaFilterExpandPlot 

# TargetDataPlotFacet <- TargetDataMeta %>% ggplot() +
#   geom_point(aes(x = time, y = OD680, colour = as.factor(WL)), size = 0.1) +
#   geom_point(aes(x = time, y = Actinic_par/1000),  colour = "orange", size = 0.0001) +
#   scale_x_continuous(breaks=seq(0, 800, by = 125)) +
#   scale_colour_manual(values = MCMIXColours) +
#   labs(y = "Optical Density 680nm (OD680)", x = "Elapsed Time (h)") +
#   facet_grid(rows = vars(as.factor(O2)), cols = vars(as.factor(Par_ue),Strain, as.factor(Tube))) +
#   theme_bw() +  
#   labs(colour = "Actinic PAR (nm)")

```

## Save filtered preliminary plot if desired

```{r save filtered preliminary plot as .png to folder}
# 
#  ggsave(file = file.path(PlotsPath, paste(TargetFileName, "TargetDataMetaFilterPlot",".png",sep = "")), plot = TargetDataMetaFilterPlot, device = NULL, scale = 1, height=10, width= 20, units = c("cm"),dpi = 300, limitsize = TRUE)
# # 
#  ggsave(file = file.path(PlotsPath, paste(TargetFileName, "TargetDataMetaFilterExpandPlot",".png",sep = "")), plot = TargetDataMetaFilterExpandPlot, device = NULL, scale = 1, height=10, width= 20, units = c("cm"),dpi = 300, limitsize = TRUE)
```

```{r DailyPAR}
TargetDataMetaFilter <- TargetDataMetaFilter %>%
  mutate(SetActinic_day = case_when(LightShape == 'Sine' ~ Par_ue/2 * 3600 * Photoperiod,
                                  LightShape == 'Square' ~ Par_ue * 3600 * Photoperiod))

```

Implement Daily Cumulative PAR for Corrected Actinic by numeric integration

```{r Actinic_parOD}
#generate corrected values of Actinic_par accounting for OD
#correction assumes true 100% transmission through Tube + Media + Waterbath;  we could account for the 'background' OD as well if needed
#correction assumes that OD is attributable solely to change in culture suspension
#correction does not account for different absorbance of different incident light coloures
TargetDataMetaFilter <- TargetDataMetaFilter %>%
  mutate(ActinicMin_parOD680 = Actinic_par * (10^-OD680),
         ActinicMid_parOD680 = Actinic_par * (10^-(OD680*0.5)),
         ActinicMin_parOD720 = Actinic_par * (10^-OD720),
         ActinicMid_parOD720 = Actinic_par * (10^-(OD720*0.5)))

#generate daily photon dose umol photon m-2 d-1 after accounting for attenuation
TargetDataMetaFilter <- TargetDataMetaFilter %>%
  group_by(MC, Tube, Day) %>%
  mutate(ActinicMid_intervalOD720 = ActinicMid_parOD720 * ((time - dplyr::lag(time)) * 3600),
         ActinicMid_dayOD720 = sum(ActinicMid_intervalOD720, na.rm = TRUE))

``` 

```{r filterdataplotexpandActinicMid_parOD720}
#labelling dynamically offset from data traces.
#use 'median' for 'x' and OD680 + offset for 'y'
ExpandTube = 5
OD680_x = median(TargetDataMetaFilter$time)
OD720_x = median(TargetDataMetaFilter$time) + 100
Light_x = max(TargetDataMetaFilter$time) + 72

OD680_y = as.numeric(TargetDataMetaFilter %>% ungroup() %>% filter(Tube == ExpandTube, time == OD680_x) %>% select(OD680)) + 2.2

OD720_y =  as.numeric(TargetDataMetaFilter %>% ungroup() %>% filter(Tube == ExpandTube, time == OD720_x) %>% select(OD720)) + 1.1

Light_y = as.numeric(TargetDataMetaFilter %>% ungroup() %>% filter(Tube == ExpandTube, time == OD680_x) %>% select( Actinic_par))/1000 + 0.15

TargetDataMetaFilter %>% 
  filter(Tube == ExpandTube) %>%
  ggplot() +
  geom_point(aes(x = time, y = OD680, colour = as.factor(WL)), size = 0.1) +
  geom_point(aes(x = time, y = OD720), size = 0.1, alpha = 0.1, colour = "black") +
  scale_colour_manual(values = MCMIXColours) +
  geom_point(aes(x = time, y = ActinicMid_parOD720/100), colour = "orange",  size = 0.0001) +
  geom_point(aes(x = time, y = ActinicMid_dayOD720/100000), colour = "red",  size = 0.0001) +
  scale_x_continuous(breaks=seq(0, 400, by = 125)) +
  coord_cartesian(xlim = c(0, 400)) +
  labs(y = "Optical Density (OD)", x = "Elapsed Time (h)",subtitle = "Growth Light (µE); Strain; ID; Tube") +
  facet_grid(rows = vars(O2), cols = vars(Par_ue, Strain, ID, Tube)) +
  annotate(geom = "text", x = OD680_x, y = OD680_y, label = "OD680", size = 5, colour = "darkblue") +
  annotate(geom = "text", x = OD720_x, y = OD720_y, label = "OD720", size = 5, colour = "black") +
  annotate(geom = "text", x = Light_x, y = Light_y, label = "Light level", size = 5, colour = "orange") +
  theme_bw() +
  labs(colour = "Actinic PAR (nm)")+ 
  guides(colour = guide_legend(override.aes = list(size = 3,  alpha = 1))) 


```

# Save .Rds of Imported Data from TargetFile

```{r save Rds of imported data}
saveRDS(object = TargetDataMetaFilter, file = file.path(DataOut, paste(TargetFileName, "TargetDataMetaFilter.Rds",  sep = "_")), ascii = FALSE, version = NULL,
        compress = TRUE, refhook = NULL)
```
